---
title: "Regression Models Course Project"
author: "Francisco Martín"
date: "October 17, 2018"
output: html_document
fig_width: 5 
fig_height: 3.5
---


## Statement

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, 
they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). 
They are particularly interested in the following two questions:

- "Is an automatic or manual transmission better for MPG"
- "Quantify the MPG difference between automatic and manual transmissions"

## Executive Summary

We have to examine mtcars dataset (default in R) and explore how MPG is correlated with other car 
parameters such as the number of cylinders, horsepower, and automatic/manual transmission. In the end, 
we should be capable of giving an answer of how the type of transmission affects on miles per gallon 
using only linear regression analysis and give a set of figures which support our conclusions.

## Exploratory Analysis

First of all, we should load mtcars dataset into our workspace

```{r dataset}
data(mtcars)
head(mtcars)
```

As we see, type of transmission is displayed in column "am", where 1 means automatic and 0 means manual 
transmission. I don't like how it looks, so I am going to change it to a factor column and see how data 
looks for each of one:

```{r correlations, echo=FALSE}
correlations <- round(cor(mtcars)[1,],2)
```

```{r transmission_type}
mtcars_cool <- mtcars
mtcars_cool$am <- factor(mtcars$am, labels = c("manual","automatic"))
summary(mtcars_cool[mtcars_cool$am == "automatic",]$mpg)
summary(mtcars_cool[mtcars_cool$am == "manual",]$mpg)
```
```{r difference, echo=FALSE}
difference <- round(mean(mtcars_cool[mtcars_cool$am == "automatic",]$mpg)-mean(mtcars_cool[mtcars_cool$am == "manual",]$mpg),2)
```

We can see mean value is about `r difference` more mpg in automatic than in manual (plot 1). We can adventure and 
do a big linear model looking for relations, but maybe it is better to look at correlations between different 
variables and mpg before doing any model:

```{r correlations2, echo=FALSE}
correlations
```

There are four variables which have a stronger correlation. Those are "wt", "cyl", "disp" and "hp". 
Let's look how this variables and type of transmission affect on miles per galon doing different models:

```{r linear_models}
lm_1 <- lm(formula = mpg ~ am, data = mtcars)
lm_2 <- lm(formula = mpg ~ am + wt, data = mtcars)
lm_3 <- lm(formula = mpg ~ am + wt + cyl, data = mtcars)
lm_4 <- lm(formula = mpg ~ am + wt + cyl + disp, data = mtcars)
lm_5 <- lm(formula = mpg ~ am + wt + cyl + disp + hp, data = mtcars)
lm_all <- lm(formula = mpg ~ ., data = mtcars)
```

We have trained six models. Let's compare all of them using anova:

```{r anova_compare}
anova(lm_1, lm_2, lm_3, lm_4, lm_5, lm_all)
```

Looking at summary we can see how this models fit our data. Looking at the coefficient for 
type of transmission: in lm_3 coef is `r summary(lm_3)$coef[2,1]`, in lm_4 coef is `r summary(lm_4)$coef[2,1]` 
and ini lm_5 is `r summary(lm_5)$coef[2,1]`. Looks like hp is a key factor, because it changes the sign of 
the estimate am. Looking at this, and seing that wt and cyl has the same impact on model, let's train the final model:

```{r final_lm}
lm_final <- lm(formula = mpg ~ am + wt + hp, data = mtcars)
summary(lm_final)
```

Looking at R-Squared term, it explains `r round(summary(lm_final)$r.squared*100,2)`% of the variability. 
We can use this model to predict and explain general behaviour of mpg as we did in appendix (plots 2 and 3)
doublechecking residuals and seing their are normally distributed.

Once we have doublecheck this model is valid, we can conclude automatic cars will run aproximatelly 
`r round(summary(lm_final)$coef[2,1],2)` more miles per galeon.



## Conclusion

Looking at results obtained, we can conclude automatic car will travel `r round(summary(lm_final)$coef[2,1],2)` 
more miles per galeon. Based on this result, we can conclude that automatic cars are more efficient than 
manual cars.


## Apendix (figures)

### Plot 1 - BoxPlot of mpg per type of transmission

```{r plot1}
boxplot(mpg ~ am, data = mtcars_cool, col = (c("red","blue")), ylab = "Miles Per Gallon", xlab = "Transmission Type")
```

### Plot 2 - Correlation of variables in final model

```{r plot2}
mtcarsplot <- mtcars[,c(1,2,3,4,6,9)]
pairs(mtcarsplot, panel = panel.smooth, col = 9 + mtcarsplot$wt)
```

### Plot 3 - Plot of residuals in final model 

```{r plot3}
par(mfrow = c(2,2))
plot(lm_final)
```
